Compare internal vs pooled references: SCPCP000015

### 2025-06-03 analyses/infercnv-consensus-cell-type/exploratory-notebooks/03_ewings-pooled-internal.Rmd
fig size

```{r message = FALSE, warning = FALSE, fig.height = 6}
unique(infercnv_df$reference_cell_group) |>
  purrr::map(plot_cnv_distributions, infercnv_df)
```

>>>>

```{r message = FALSE, warning = FALSE, fig.width = 8}
unique(infercnv_df$reference_cell_group) |>
  purrr::map(plot_cnv_distributions, infercnv_df)
```
